---
title: "Report COVID19 Imperial Model"
author: "Måns Magnusson"
date: '2020-04-29'
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(covid19imperial)
library(ggplot2)
library(bayesplot)
m <- list()
m[[1]] <- mget(load("../results/base_general_speed-model1_base-stanfit.Rdata"))
m[[2]] <- mget(load("../results/base_general_speed-model2-stanfit.Rdata"))
m[[3]] <- mget(load("../results/base_general_speed-model3-stanfit.Rdata"))

countries <- get_countries(m[[2]]$stan_data)

```

## Summary / Take Away

- Using the increased number of covariates (model2) seem to be better, model-wise compared to baseline. 
- There seem to be something problematic with the lockdown variable in model 1. The new model from the Imperial Collage group include an hiearchical prior here to accomodate different effects.

Current flaws to be fixed:

- IFR for Finland now set to IFR for Sweden
- Data only until the 10th of April.

Potential ways forward:

- Use hospitalizations instead of deaths. I think this has better quality and is more data.
- Focus on Finland (and Sweden) at county level, although data may be missing.
- Include serological studies to estimate cumulative infections, weekly.
- Include mobility data both together with other covariates as a single factor.
- Update data, ecdc and Oxford (until today instead of 10th of April)
- Test different alpha priors


### Model descriptions

- Model 1: The baseline model, previously included, without partial pooling (the most recent model)
- Model 2: The model using S1 - S7 oxford variables
- Model 3: The model using SeverityIndex (continous variable) 

### Oxford covariate descriptions

- S1: School closing
- S2: Workplace closing
- S3: Cancel public events
- S4: Close public transport
- S5: Public information Campagins
- S6: Restrictions on internal movement (1 = General, 0 = geographic)



## Covariate effects

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- c(1,2)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_covariate_size_effects(mod$fit, mod$stan_data) + ggtitle(paste0("Model", plot_models[i]))
  suppressWarnings(print(p))
}

```



## R0 for different countries

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_mu(mod$fit, mod$stan_data, countries) + ggtitle(paste0("Model", plot_models[i]))
  print(p)
}
```


## Infectious, deaths and Rt

```{r, include=TRUE, fig.width=12, fig.height=4}
plot_models <- 1:length(m)
countries <- get_countries(m[[1]]$stan_data)
for(country in countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_three_panel(country = country, stan_fit = mod$fit, stan_data = mod$stan_data, daily_data = mod$daily_data, title = paste0(country, ": Model", plot_models[i]))
    print(p)
  }
}

```

## Stan code

```{r, include=TRUE, fig.width=12, fig.height=4}
print(m[[1]]$fit@stanmodel)

#plot_models <- 1:length(m)
#for(i in seq_along(plot_models)){
#  print(paste0(" ######## MODEL", i, " ######## "))
#  print(m[[i]]$fit@stanmodel)
#}

```
