---
title: "Report: COVID19 Bayesian Epidemiological Model"
author: "Måns Magnusson"
date: '2020-05-11'
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(covid19model)
library(ggplot2)
library(bayesplot)
m <- list()
m[[1]] <- mget(load("../results/model1b_0430-stanfit.Rdata"))
m[[2]] <- mget(load("../results/model2b_0430-stanfit.Rdata"))
m[[3]] <- mget(load("../results/model4b_0430-stanfit.Rdata"))
m[[4]] <- mget(load("../results/model3b_0430-stanfit.Rdata"))
m[[5]] <- mget(load("../results/model7b_0430-stanfit.Rdata"))

countries <- get_countries(m[[1]]$stan_data)
case_countries <- c("Finland", "Sweden", "Italy")
noncase_countries <- countries[!countries %in% case_countries]
```

### Model descriptions

- Model 1: The Imperial College model v3, with partial pooling of lockdown variable
- Model 2: Google Mobility and Oxford Binary Intervention indicators. Regression coefficients are assumed common for all countries (pooled alpha).
- Model 3: Google Mobility and Oxford Binary Intervention indicators. Regression coefficients are hierarchical and inform each other between countries. (hierarchical alpha)
- Model 4: Google Mobility and Oxford Binary Intervention indicators. Regression coefficients are estimated for each country. (local alpha)
- Model 5: Google Mobility, Oxford Binary Intervention indicators and b-spline. Regression coefficients are hierarchical and the b-spline is a local spline over t per country.

### Oxford covariate descriptions

- C1: School closing
- C2: Workplace closing
- C3: Cancel public events
- C4: Restrictions on Gatherings
- C5: Close public transport
- C6: Stay at home requirements
- H2: Testing policy

# Case study: The Sweden, Finland and Italy

All other countries are included in the Appendix.

## Global covariate effects (model 1 and 2)

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:2

for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_covariate_size_effects(mod$fit, mod$stan_data) + ggtitle(paste0("Model", plot_models[i]))
  suppressWarnings(print(p))
}

```


## Country specific effects (model 3 and 4)

We see that the hierarchical model has an easier time to capture the general effect that mobility has a larger effect than the stringency index. Hence the actual mobility affects $R_t$ more than the interventions.

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 3:4

for(country in case_countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_covariate_size_effects_country(country, mod$fit, mod$stan_data) + ggtitle(paste0(country, ", Model", plot_models[i]))
    suppressWarnings(print(p))
  }
}


```


## R0 for different countries

We can see that the different values for R0 vary much more between the countries when we use models with common regression coefficients.

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_mu(mod$fit, mod$stan_data, countries) + ggtitle(paste0("Model", plot_models[i]))
  print(p)
}
```



## Infections, cases, deaths and Rt by country and model

```{r, include=TRUE, fig.width=12, fig.height=4}
plot_models <- 1:length(m)
for(country in case_countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_three_panel(country = country, stan_fit = mod$fit, stan_data = mod$stan_data, daily_data = mod$daily_data, title = paste0(country, ": Model", plot_models[i]))
    print(p)
  }
}



```

## Stan code

```{r, include=TRUE, fig.width=12, fig.height=4}
print(m[[1]]$fit@stanmodel)

#plot_models <- 1:length(m)
#for(i in seq_along(plot_models)){
#  print(paste0(" ######## MODEL", i, " ######## "))
#  print(m[[i]]$fit@stanmodel)
#}

```


# Appendix

## Country specific effects (model 3 to 4)

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 3:4

for(country in noncase_countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_covariate_size_effects_country(country, mod$fit, mod$stan_data) + ggtitle(paste0(country, ", Model", plot_models[i]))
    suppressWarnings(print(p))
  }
}

```


## Infections, cases, deaths and Rt by country and model

```{r, include=TRUE, fig.width=12, fig.height=4}
plot_models <- 1:length(m)
for(country in noncase_countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_three_panel(country = country, stan_fit = mod$fit, stan_data = mod$stan_data, daily_data = mod$daily_data, title = paste0(country, ": Model", plot_models[i]))
    print(p)
  }
}

```

### Reproducibility

Report git hash: 
```{r, include=TRUE, fig.width=12, fig.height=4}
cat(system("git rev-parse HEAD", intern=TRUE))
```
