---
title: "Report COVID19 Model"
author: "Måns Magnusson"
date: '2020-05-05'
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(covid19imperial)
library(ggplot2)
library(bayesplot)
m <- list()
m[[1]] <- mget(load("../results/model1_0430-stanfit.Rdata"))
m[[2]] <- mget(load("../results/model1b_0430-stanfit.Rdata"))
m[[3]] <- mget(load("../results/model6a_0430-stanfit.Rdata"))
m[[4]] <- mget(load("../results/model5a_0430-stanfit.Rdata"))
m[[5]] <- mget(load("../results/model5c_0430-stanfit.Rdata"))
m[[6]] <- mget(load("../results/model6b_0430-stanfit.Rdata"))

countries <- get_countries(m[[1]]$stan_data)

```

## Summary / Take Away

- Using the increased number of covariates seem to be better, model-wise compared to baseline. I think in many istuations our models now perform better than Imperial College Londons baseline.
- Mobility on transit station seem to be a good covariate to use. 
- The regression coefficients are really sensitive. They need to be bounded for the model not to explode. 


### Current flaws to be fixed:

- IFR for Finland now set to IFR for Sweden


### Potential ways forward:

- Use hospitalizations instead of deaths. I think this has better quality and is more data.
- Focus on Finland (and Sweden) at county level, although data may be missing.
- Include serological studies to estimate cumulative infections, weekly.
- Partial pooling of mobility variables.


### Model descriptions

- Model 1: The baseline model, without partial pooling of lockdown
- Model 2: The baseline model, with partial pooling of lockdown variable
- Model 3: Using Oxford Response data as indicator variables
- Model 4: Google Mobility in transit stations 
- Model 5: Google Mobility in transit stations and SeverityIndex 
- Model 6: Google Mobility in transit stations and Oxford Binary data

### Oxford covariate descriptions

- C1: School closing
- C2: Workplace closing
- C3: Cancel public events
- C4: Restrictions on Gatherings
- C5: Close public transport
- C6: Stay at home requirements
- H2: Testing policy


## Covariate effects

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_covariate_size_effects(mod$fit, mod$stan_data) + ggtitle(paste0("Model", plot_models[i]))
  suppressWarnings(print(p))
}

```



## R0 for different countries

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_mu(mod$fit, mod$stan_data, countries) + ggtitle(paste0("Model", plot_models[i]))
  print(p)
}
```


## Infections, deaths and Rt by country and model

```{r, include=TRUE, fig.width=12, fig.height=4}
plot_models <- 1:length(m)
countries <- get_countries(m[[1]]$stan_data)
for(country in countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_three_panel(country = country, stan_fit = mod$fit, stan_data = mod$stan_data, daily_data = mod$daily_data, title = paste0(country, ": Model", plot_models[i]))
    print(p)
  }
}

```

## Stan code

```{r, include=TRUE, fig.width=12, fig.height=4}
print(m[[1]]$fit@stanmodel)

#plot_models <- 1:length(m)
#for(i in seq_along(plot_models)){
#  print(paste0(" ######## MODEL", i, " ######## "))
#  print(m[[i]]$fit@stanmodel)
#}

```
