---
title: "Report COVID19 Model"
author: "Måns Magnusson"
date: '2020-05-05'
output: 
  pdf_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(covid19imperial)
library(ggplot2)
library(bayesplot)
m <- list()
m[[1]] <- mget(load("../results/model4a_0430-stanfit.Rdata"))
m[[2]] <- mget(load("../results/model5a_0430-stanfit.Rdata"))
m[[3]] <- mget(load("../results/model5b_0430-stanfit.Rdata"))

countries <- get_countries(m[[1]]$stan_data)

```

## Summary / Take Away

- It is possible to include b-splines in the model.
- It does not seem to give a lot of gains with using b-splines compare to linear effects.
- Using splines for t is working well to capture the underlying change in Rt, although, this should be needed to be different for different countries.

### Model descriptions

- Model 1: Splines on t, the time point
- Model 2: Linear neg_log_transit_proportion
- Model 3: Splines on neg_log_transit_proportion

## Covariate effects

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_covariate_size_effects(mod$fit, mod$stan_data) + ggtitle(paste0("Model", plot_models[i]))
  suppressWarnings(print(p))
}

```



## R0 for different countries

```{r, include=TRUE, fig.width=7, fig.height=3}
plot_models <- 1:length(m)
for(i in seq_along(plot_models)){
  mod <- m[[plot_models[i]]]
  p <- plot_mu(mod$fit, mod$stan_data, countries) + ggtitle(paste0("Model", plot_models[i]))
  print(p)
}
```


## Infections, deaths and Rt by country and model

```{r, include=TRUE, fig.width=12, fig.height=4}
plot_models <- 1:length(m)
countries <- get_countries(m[[1]]$stan_data)
for(country in countries){
  for(i in seq_along(plot_models)){
    mod <- m[[plot_models[i]]]
    p <- plot_three_panel(country = country, stan_fit = mod$fit, stan_data = mod$stan_data, daily_data = mod$daily_data, title = paste0(country, ": Model", plot_models[i]))
    print(p)
  }
}

```

## Stan code

```{r, include=TRUE, fig.width=12, fig.height=4}
print(m[[1]]$fit@stanmodel)

#plot_models <- 1:length(m)
#for(i in seq_along(plot_models)){
#  print(paste0(" ######## MODEL", i, " ######## "))
#  print(m[[i]]$fit@stanmodel)
#}

```
